Assembly Quality Metrics - Quast Results

### 2019-04-24 notebooks/assembly_metrics.Rmd
minor changes

isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F) %>%
  filter(id %not_in% c("2016-17-565-1-S",
                       "2016-02-428-2-S",
                       "2016-02-486-2-S",
                       "2016-02-732-2-S",
                       "2014-01-1741-1-S"))

@@

df_clean <- create_df(df) %>%
  filter(grepl("broken", Assembly) == FALSE) %>%
  filter(Assembly %not_in% c("51-2016-02-486_S31_pilon_spades",
                             "68-2016-17-565_S45_pilon_spades",
                             "52-2016-02-732_S43_pilon_spades",
                             "50-2016-02-428_S19_pilon_spades",
                             "4-2014-01-1741_TAAGGCGA-ACTGCATA_pilon_spades")) %>%
  mutate(ref = Assembly %>%
           gsub("_pilon_spades", "", .)) %>%
  left_join(id_data, by = "ref") %>%
  left_join(isolate_data[c("id","sequencer")], by = "id")

@@

# Mean metrics
```{r}
print(paste0("Mean number of contigs: ", round(mean(metrics2$no_of_contigs), 1)))
print(paste0("Mean size of largest contigs: ", round(mean(metrics2$largest_contig), 1)))
print(paste0("Mean N50: ", round(mean(metrics2$N50), 1)))
print(paste0("Mean NG50: ", round(mean(as.numeric(metrics2$NG50)), 1)))

@@

# Summarised assembly stats
## Summary stats per animal species
```{r}
p1 <- ggplot(metrics2, aes(species, N50)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p2 <- ggplot(metrics2, aes(species, no_of_contigs)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of contigs") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p3 <- ggplot(metrics2, aes(species, largest_contig)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "Largest contig") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p4 <- ggplot(metrics2, aes(species, as.numeric(no_of_misassemblies))) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of misassemblies") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

@@

## Summary stats per sequencing method
```{r}
p5 <- ggplot(metrics2, aes(sequencer, N50)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p6 <- ggplot(metrics2, aes(sequencer, no_of_contigs)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of contigs") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p7 <- ggplot(metrics2, aes(sequencer, largest_contig)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "Largest contig") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p8 <- ggplot(metrics2, aes(sequencer, as.numeric(no_of_misassemblies))) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of misassemblies") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

>>>>

isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F) %>%
  filter(id %not_in% c("2016-17-565-1-S",
                       "2016-02-428-2-S",
                       "2016-02-486-2-S",
                       "2016-02-732-2-S"))

@@

df_clean <- create_df(df) %>%
  filter(grepl("broken", Assembly) == FALSE) %>%
  filter(Assembly %not_in% c("51-2016-02-486_S31_pilon_spades",
                             "68-2016-17-565_S45_pilon_spades",
                             "52-2016-02-732_S43_pilon_spades",
                             "50-2016-02-428_S19_pilon_spades")) %>%
  mutate(ref = Assembly %>%
           gsub("_pilon_spades", "", .)) %>%
  left_join(id_data, by = "ref") %>%
  left_join(isolate_data[c("id","sequencer")], by = "id")

@@

# Mean metrics
```{r}
metrics3 <- filter(metrics2, id != "2014-01-1741-1-S")

print(paste0("Mean number of contigs: ", round(mean(metrics3$no_of_contigs), 1)))
print(paste0("Mean size of largest contigs: ", round(mean(metrics3$largest_contig), 1)))
print(paste0("Mean N50: ", round(mean(metrics3$N50), 1)))
print(paste0("Mean NG50: ", round(mean(as.numeric(metrics3$NG50)), 1)))

@@

# Summarised assembly stats
## Summary stats per animal species
```{r}
p1 <- ggplot(metrics3, aes(species, N50)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p2 <- ggplot(metrics3, aes(species, no_of_contigs)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of contigs") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p3 <- ggplot(metrics3, aes(species, largest_contig)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "Largest contig") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p4 <- ggplot(metrics3, aes(species, as.numeric(no_of_misassemblies))) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of misassemblies") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

@@

## Summary stats per sequencing method
```{r}
p5 <- ggplot(metrics3, aes(sequencer, N50)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p6 <- ggplot(metrics3, aes(sequencer, no_of_contigs)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of contigs") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p7 <- ggplot(metrics3, aes(sequencer, largest_contig)) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "Largest contig") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))

p8 <- ggplot(metrics3, aes(sequencer, as.numeric(no_of_misassemblies))) +
  stat_boxplot(geom = "errorbar", width = 0.4) +
  geom_boxplot() +
  labs(y = "No. of misassemblies") +
  scale_y_continuous(labels = comma) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 8))
